\sysfull

### 2018-04-17 paper/intro.tex
Final pass on intro and background

\begin{wrapfigure}{t!}{0.4\textwidth}
    \centering
    \includegraphics[width=0.4\textwidth]{figures/intro-figure.pdf}
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{cmt} in the figure). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{wrapfigure}

@@

\textbf{Contributions.} To summarize, \sys's main contributions are: 
%
\begin{itemize}
\item The first {\em adaptive} task-based intermittent execution model that
dynamically \emph{coalesces} tasks to reduce commit overhead and
\emph{downscales} tasks to ensure forward progress.
\item The first memory virtualization mechanism that preserves the atomicity of coalesced tasks under power failures.
%\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.
\item A fully-realized prototype of \sys that runs on real energy-harvesting devices, to be released as open source after publication via~\cite{coala_website}. 
\item An evaluation directly comparing \sys to a state of the art task-based
intermittent programming and execution model from prior work, showing that on a
suite of benchmarks from the literature and several new workloads, \sys often
has higher performance and is more flexible to diverse energy conditions. 
\end{itemize}
%
Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while
Sections~\ref{sec:task_adaptation} describe \sys's task adaptation mechanism (coalescing and downscaling). Memory virtualization mechanism is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are give in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the
context of related work and Section~\ref{sec:conclusions} concludes and discusses
future work.

>>>>

\begin{wrapfigure}{t!}{0.45\textwidth}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/intro-figure.pdf}
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{cmt} in the figure). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{wrapfigure}

@@

\textbf{Contributions.} To summarize, \sys's main contributions are: 
%
\begin{itemize}
\item The first {\em adaptive} task-based intermittent execution model that
dynamically \emph{coalesces} tasks to reduce commit overhead and
\emph{downscales} tasks to ensure forward progress.
\item The first memory virtualization mechanism that preserves the atomicity of coalesced tasks under power failures.
%\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.
\item A fully-realized prototype of \sys that runs on real energy-harvesting devices, to be released as open source after publication via~\cite{coala_website}. 
\item An evaluation directly comparing \sys to a state of the art task-based
intermittent programming and execution model from prior work, showing that on a
suite of benchmarks from the literature and several new workloads, \sys often
has higher performance and is more flexible to diverse energy conditions. 
\end{itemize}
%
Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while
Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism (coalescing and downscaling). Memory virtualization mechanism is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the
context of related work and Section~\ref{sec:conclusions} concludes and discusses
future work.
